\documentclass[12pt]{resume}    
\usepackage[left=0.5in,top=0.75in,right=0.5in,bottom=0.75in]{geometry} 
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{xcolor}

\name{Chen(Cici) Ling}
% \address{Boston, Massachusetts}
\address{ 
% (+1) 857-763-7756        
\href{https://ciciling.com}{ciciling.com}           
ccling@iu.edu 
% \href{mailto:ccling@bu.edu}{Email} \\ 
% \href{https://twitter.com/ciciling07}{Twitter} \\
% \href{https://ciciling.com/}{Website} \\
% \href{https://github.com/ciciling07}{Github} \\
% \href{https://www.linkedin.com/in/chen-ling-1a7b276a/}{Linkedin} \\
% \href{https://scholar.google.com/citations?user=i9KCc1cAAAAJ&hl=en}{Google Scholar}
}

\begin{document}
\begin{center}
\textbf{Assistant Professor in the\\
Luddy School of Informatics, Computing, and Engineering\\
at Indiana University Bloomington}
\end{center}

% My research interests are broadly in the areas of security, privacy, and human-computer interaction.
% My research aims to better understand and mitigate online abusive behavior using multi-modal, multi-platform, and mixed-method approaches.
% My work has been published in top-tier journals and conferences, including{ \href{https://www.computer.org/csdl/proceedings-article/sp/2021/893400b047/1t0x8Vq5Zde}{IEEE S\&P}},{ \href{https://dl.acm.org/doi/abs/10.1145/3449155}{ACM CSCW}},{ \href{https://ojs.aaai.org/index.php/ICWSM/article/view/22168}{AAAI ICWSM}}, and has been reported by{ \href{https://www.wired.com/story/zoombomb-inside-jobs/}{Wired}, { \href{https://www.newscientist.com/article/2255550-most-zoombombing-is-not-done-by-external-hackers-theyre-inside-jobs/}{New Scientist}}, and{ \href{https://www.washingtonpost.com/technology/2020/04/08/coronavirus-spreads-so-does-online-racism-targeting-asians-new-research-shows/}{The Washington Post}}. 
% I am the recipient of the{ \href{https://research.facebook.com/fellows/ling-cheng/}{2022 Meta PhD fellowship}} in Security and Privacy,{ \href{https://www.bu.edu/hic/profile/chen-ling/}{a Hariri student Fellow}} at Boston University, and was a visiting scholar at Max Planck Institute supported by a fellowship.



\medskip

% \end{rSection}
% \medskip
% \clearpage
% \begin{rSection}{Positions}
% \item \textbf{Indiana University Bloomington}\\
% Assistant Professor \hfill 2024 - present\\
% Luddy School of Informatics, Computing, and Engineering \hfill Bloomington, Indiana
% \item \textbf{Boston University}\\
% The Security Lab\\
% Research Assistant \hfill 2019 – 2024
% \\Advisor: Prof. Gianluca Stringhini \hfill Boston, USA

% \item \textbf{Max-Planck-Institute for Informatics}\\ 
% Research Group Internet Architecture (INET) \\
% Visiting Scholar 
% \hfill 2021
% \\Advisor: Prof. Krishna Gummadi, Prof. Savvas Zannettou
% \hfill Saarbr{\"u}cken, Germany

% \item \textbf{Beijing Normal University}\\
% Institute of Developmental Psychology\\
% Research Assistant \hfill 2017 – 2018
% \\Advisor: Prof. Xiaoyi Fang \hfill Beijing, China
% % \item \textbf{Six Capital} \hfill 2015 - 2017
% % \\Trading Analyst \hfill Singapore

% \end{rSection}


\begin{rSection}{Education \& Training}
\item \textbf{Ph.D., Computer Engineering} \hfill Sep. 2019 - May 2024
\\Boston University \hfill Boston, MA\\
% \\{Advisor: Gianluca Stringhini}
{Advisor: Prof. Gianluca Stringhini}

\item \textbf{Visiting Scholar}\\ 
Max Planck Institute for Informatics \hfill 2021\\
Research Group Internet Architecture (INET) \hfill Saarbr{\"u}cken, Germany
\\Advisor: Prof. Krishna Gummadi, Prof. Savvas Zannettou


\item \textbf{M.S., Computer Science} \hfill May 2018 - Aug. 2019
\\University of Illinois Urbana-Champaign \hfill Urbana, IL

\item \textbf{Research Assistant}\\
Beijing Normal University\hfill 2017 – 2018\\
Institute of Developmental Psychology\hfill Beijing, China
\\Advisor: Prof. Xiaoyi Fang 

\item \textbf{B.A., Art History} \hfill Aug. 2011 - Jul. 2015
\\Tsinghua University \hfill Beijing, China
\end{rSection}

\medskip

\begin{rSection}{Grants \& Awards}
\item IEEE S\&P 2024 Student Travel Grant (\$1,200) \hfill 2024
\item SWE Student Travel Grant \hfill  2023
\item EECS Rising Star (selection rate: 101/288 = 35\%) \hfill 2023\\
\href{https://eecsrisingstars2023.cc.gatech.edu/participants/Chen_Ling/}{[Media Coverage]}
\item Meta PhD Research Fellowship (\$84,000, selection rate: 37/2300 = 1.6\%) \hfill  2022 - 2024\\
\href{https://research.facebook.com/fellows/ling-cheng/}{[Media Coverage]}
\item ACM Web Science Conference Registration Grant (\$150) \hfill 2023
\item IEEE S\&P Student Registration Grant (\$150) \hfill 2021
\item  Instagram Research Awards (Co-PI, \$50,000) \hfill  2021\\
% Instagram research awards on safety and community health:\\ 
Towards proactive moderation of coordinated harassment on Instagram\\
\href{https://research.facebook.com/blog/2021/12/announcing-the-recipients-of-instagram-research-awards-on-safety-and-community-health/}{[Media Coverage]}
\item 
Hariri Graduate Student Fellowship (\$6,300) \hfill 2021\\
\href{https://www.bu.edu/hic/profile/chen-ling/}{[Media Coverage]} 
\item Max Planck Institute Fellowship (\$5,000) \hfill 2021
\item Boston University Distinguished Computer Engineering Fellowship (\$37,000) \hfill 2019
\item National Undergraduate Academic Science and Technology Race Challenge
Cup Award (\$1,500) \hfill 2015
\item Tsinghua Scholarship for Comprehensive Excellence (\$1,000) \hfill 2014
\item Tsinghua X-lab Entrepreneurship Fund (\$7,500) \hfill 2014
\item Tsinghua Student Research Training Program Grant (\$2,000) \hfill 2012, 2013
\item National Innovation and Entrepreneurship Association (\$1,500) \hfill 2011
\end{rSection}

% \begin{rSection}{Grants \& Awards}
% \item ACM Web Science Conference Registration Grant (\$150) \hfill 2023

% \item IEEE S\&P Student Registration Grant (\$150) \hfill 2021
% \item National Undergraduate Academic Science and Technology Race Challenge
% Cup Award (\$1,500) \hfill 2015
% \item Tsinghua Scholarship for Comprehensive Excellence (\$1,000) \hfill 2014
% \item National Innovation and Entrepreneurship Association (\$1,500) \hfill 2011
% \end{rSection}

\medskip

% {\color{mediumblue} \MakeUppercase{\textbf{ \huge Publications } } }

% conference pub
\MakeUppercase{\textbf{Peer Reviewed Publications}} (* = equal contribution)
\sectionlineskip
\renewcommand{\labelenumi}{\padzeroes[2]{\decimalnum{\theenumi}}.}
\hrule height .7pt % Horizontal line
\begin{etaremune}[leftmargin=.6in]

    \item \paperabbrev{USENIX Security '24} Paudel, P., \textbf{Ling, C.}, Blackburn, J., and Stringhini, G.
     \newline \textit{PIXELMOD: Improving Soft Moderation of Visual Misleading Information on Twitter.}
     \newline USENIX Security Symposium, 2024.
     
    \item \paperabbrev{CSCW '23} Wang, Y., \textbf{Ling, C.}, and Stringhini, G.
     \newline \textit{Understanding the Use of Images to Spread COVID-19 Misinformation on Twitter.}
     \newline Proceedings of the ACM on Human-Computer Interaction, 7(CSCW), 2023.
     \newline [\href{https://dl.acm.org/doi/pdf/10.1145/3579542}{Paper}]

     \item \paperabbrev{CSCW '23} Ali, S., Razi, A., Kim, S., \textbf{Ling, C.}, De Choudhury Munmun, Wisniewski, P. J., and Stringhini, G.
    \newline \textit{Getting Meta: A Multimodal Approach for Detecting Unsafe Conversations within Instagram Direct Messages of Youth.}
    \newline Proceedings of the ACM on Human-Computer Interaction, 7(CSCW), 2023. 
    \newline [\href{https://seclab.bu.edu/people/gianluca/papers/risks-cscw2023.pdf}{Paper}]
    
    \item \textbf{[EuroS\&P '23]} 
    Singhal, M., \textbf{Ling, C.}, Kumarswamy, N., Stringhini, G., and Nilizadeh, S.
    \newline \textit{SoK: content moderation in social media, from guidelines to enforcement, and research to practice.}
    \newline IEEE European Symposium on Security and Privacy, 2023 
    \newline [Acceptance rate: 29\%]
    \newline [\href{https://arxiv.org/pdf/2206.14855}{Paper}]
    
    \item \textbf{[WebSci '23]} Balci, U., \textbf{Ling, C.}, Squire, M., De Cristofaro, E., Stringhini, G., and Blackburn, J.
    \textit{Beyond Fish and Bicycles: Exploring the Varieties of Online Women's Ideological Spaces.} 
    \newline The 15th ACM Web Science Conference, 2023. 
    \newline [Acceptance rate: 30\%]
    \newline [\href{https://arxiv.org/pdf/2303.07099.pdf}{Paper}]

    \item \paperabbrev{ICWSM '23} 
    \textbf{Ling, C.}, K. P. Gummadi, and S. Zannettou.
    \newline \textit{``Learn the Facts About COVID-19'': Analyzing the Use of Warning Labels on TikTok Videos.} 
    \newline The International AAAI Conference on Web and Social Media (ICWSM), 2022.
    \newline [Acceptance rate: 20\%]
    \newline [\href{https://arxiv.org/pdf/2201.07726.pdf}{Paper}]
    
    \item \textbf{[WebSci '22]} 
    \textbf{Ling, C.}, J. Blackburn, E. De Cristofaro, and G. Stringhini. 
    \newline \textit{Slapping Cats, Bopping Heads, and Oreo Shakes: Understanding Indicators of Virality in TikTok Short Videos.} 
    \newline The 14th ACM Web Science Conference, 2022.
    \newline [Acceptance rate: 30\%]
    \newline Media Coverage: [\href{https://www.zdnet.com/article/tiktok-doesnt-read-your-mind-it-makes-your-mind/}{ZDNet}]
    \newline [\href{https://arxiv.org/pdf/2111.02452.pdf}{Paper}]
\clearpage
      
    \item \textbf{[WWW '21]}
     F. Tahmasbi, L. Schild, \textbf{Ling, C.}, J. Blackburn, G. Stringhini, Y. Zhang, and S. Zannettou. 
     \newline \textit{``Go eat a bat, Chang!'': An Early Look on the Emergence of Sinophobic Behavior onWeb Communities in the Face of COVID-19.}
     \newline Proceedings of the ACM Web Conference, 2021. 
     \newline [Acceptance rate: 17.7\%]
     \newline Media Coverage: [\href{https://www.washingtonpost.com/technology/2020/04/08/coronavirus-spreads-so-does-online-racism-targeting-asians-new-research-shows/}{The Washington Post 1}][\href{https://www.washingtonpost.com/technology/2021/02/12/china-covid-misinformation-li-meng-yan/}{The Washington Post 2}]
     \newline [\href{https://dl.acm.org/doi/pdf/10.1145/3442381.3450024}{Paper}]
    \item \textbf{[S\&P '21]} 
    \textbf{Ling, C.*}, B. Utku*, J. Blackburn, and G. Stringhini. 
    \newline \textit{A First Look at Zoombombing.} 
    \newline The 42nd IEEE Symposium on Security and Privacy, 2021. 
    \newline [Acceptance rate: 12.08\%]
    \newline Media Coverage: [\href{https://www.newscientist.com/article/2255550-most-zoombombing-is-not-done-by-external-hackers-theyre-inside-jobs/}{New Scientist}][\href{https://www.wired.com/story/zoombomb-inside-jobs/}{Wired}][\href{https://www.eurekalert.org/news-releases/719104}{Eurek Alert}][\href{https://arstechnica.com/information-technology/2021/02/zoombombing-countermeasures-are-ineffective-in-the-vast-majority-of-cases/}{Arstechnica}][\href{https://www.insidehighered.com/news/2021/02/17/college-zoombombing-incidents-often-incited-students?utm_source=Inside+Higher+Ed&utm_campaign=8d72a05de8-DNU_2021_COPY_02&utm_medium=email&utm_term=0_1fcbc04421-8d72a05de8-198556833&mc_cid=8d72a05de8&mc_eid=5bccd444e8}{Inside Higher Ed}]\\
    \noindent[\href{https://www.helpnetsecurity.com/2021/02/09/most-zoombombing-incidents-are-inside-jobs/}{Help Net Security}][\href{https://www.publicsource.org/racist-zoom-bombing-pa-hate-what-to-do/}{Public Source}][\href{https://www.forbes.com/sites/forbestechcouncil/2022/03/28/video-security-is-more-than-just-security---its-about-brand-integrity-and-your-customer-commitments/?sh=2d79f93b663d}{Forbes}]
    \newline
    [\href{https://ieeexplore.ieee.org/stamp/stamp.jsp?arnumber=9519457}{Paper}] [\href{https://www.youtube.com/watch?v=9LSvxtqe38c}{Video Presentation}]
    
  \item \textbf{[S\&P Magazine '22]} 
    \textbf{Ling, C.*}, Utku, B.*, J. Blackburn, and G. Stringhini.
    \newline \textit{A First Look at Zoombombing.}
    \newline IEEE Security \& Privacy Magazine, 2022. \textbf{\textcolor{orange}{Invited Submission.}}
     \newline [\href{https://www.computer.org/csdl/magazine/sp/2022/02/09638984/1z98wsr8mQw}{Paper}]

    
    \item \textbf{[CSCW '21]}
   \textbf{Ling, C.}, I. AbuHilal, E. De Cristofaro, S. Zannettou, and G. Stringhini.
   \newline \textit{Dissecting the Meme Magic: Understanding Indicators of Virality in Image Memes.} 
   \newline The 23rd ACM Conference on Computer-Supported Cooperative Work and Social Computing, 2021. 
   \newline Media Coverage: [\href{https://www.inverse.com/input/culture/viral-meme-ai-study-bernie-sanders}{Input Magazine}][\href{https://www.bu.edu/articles/2021/bernie-sanders-sitting-memes-instant-popularity-explained-by-science/?utm_source=twitter&utm_medium=link&utm_content=research_computerscience&utm_campaign=social_experts}{The Brink}] 
   \newline [\href{https://dl.acm.org/doi/pdf/10.1145/3449155}{Paper}] 
    
    \item \textbf{[CySoc '20]}
    \textbf{Ling, C.} and G. Stringhini. 
    \newline \textit{Examining the Impact of Social Distance on Reactions Towards Sulli’s Death on Twitter.}
    \newline Workshop on Cyber Social Threats, ICWSM 2020. 
    \newline [\href{https://workshop-proceedings.icwsm.org/pdf/2020_15.pdf}{Paper}]
    
    \item \textbf{[ISCV '18]}
    Y. Hong, \textbf{Ling, C.} and Z. Ye. 
    \newline \textit{End-to-end soccer video scene and event classification with deep transfer learning.} 
    \newline International Conference on Intelligent Systems and Computer Vision (ISCV), 2018. 
    \newline [\href{https://ieeexplore.ieee.org/stamp/stamp.jsp?tp=&arnumber=8369043}{Paper}]

    \item \textbf{[Advance in Psychology]}
    \textbf{Ling, C.}. 
    \newline \textit{Intouchable prophecy: Enlightenment from The Nature of Prejudice in the Digital Age.} 
    \newline Advance in Psychology, 8(11), 1651-1656, 2018. \newline[\href{https://doi.org/10.12677/AP.2018.811191}{Paper}]
\end{etaremune}

\medskip

% \MakeUppercase{\textbf{Journal Publications}} (* = equal contribution)
% \sectionlineskip
% \renewcommand{\labelenumi}{J\padzeroes[2]{\decimalnum{\theenumi}}.}
% \hrule % Horizontal line
% \begin{etaremune}[leftmargin=.6in]
%      \item \paperabbrev{CSCW '23} Wang, Y., \textbf{Ling, C.}, and Stringhini, G.
%      \newline \textit{Understanding the Use of Images to Spread COVID-19 Misinformation on Twitter.}
%      \newline Proceedings of the ACM on Human-Computer Interaction, 7(CSCW), 2023.
%      \newline [\href{https://dl.acm.org/doi/pdf/10.1145/3579542}{Paper}]
     
%      \item \paperabbrev{CSCW '23} Ali, S., Razi, A., Kim, S., \textbf{Ling, C.}, De Choudhury M. U. N. M. U. N., Wisniewski, P. J., and Stringhini, G.
%     \newline \textit{Getting Meta: A Multimodal Approach for Detecting Unsafe Conversations within Instagram Direct Messages of Youth.}
%     \newline Proceedings of the ACM on Human-Computer Interaction, 7(CSCW), 2023. 
%     \newline [\href{https://seclab.bu.edu/people/gianluca/papers/risks-cscw2023.pdf}{Paper}]
    
%     \item \textbf{[S\&P Magazine '22]} 
%     \textbf{C. Ling*}, B. Utku*, J. Blackburn, and G. Stringhini.
%     \newline \textit{A First Look at Zoombombing.}
%     \newline IEEE Security \& Privacy Magazine, 2022.
%      \newline [\href{https://www.computer.org/csdl/magazine/sp/2022/02/09638984/1z98wsr8mQw}{Paper}]
    
%    \item \textbf{[CSCW '21]}
%    \textbf{C. Ling}, I. AbuHilal, E. De Cristofaro, S. Zannettou, and G. Stringhini.
%    \newline \textit{Dissecting the Meme Magic: Understanding Indicators of Virality in Image Memes.} 
%    \newline The 23rd ACM Conference on Computer-Supported Cooperative Work and Social Computing, 2021. 
%    \newline Media Coverage: [\href{https://www.inverse.com/input/culture/viral-meme-ai-study-bernie-sanders}{Input Magazine}][\href{https://www.bu.edu/articles/2021/bernie-sanders-sitting-memes-instant-popularity-explained-by-science/?utm_source=twitter&utm_medium=link&utm_content=research_computerscience&utm_campaign=social_experts}{The Brink}] 
%    \newline [\href{https://dl.acm.org/doi/pdf/10.1145/3449155}{Paper}] 
    
%     \item \textbf{[Advance in Psychology]}
%     \textbf{C. Ling}. 
%     \newline \textit{Intouchable prophecy: Enlightenment from The Nature of Prejudice in the Digital Age.} 
%     \newline Advance in Psychology, 8(11), 1651-1656, 2018. \newline[\href{https://doi.org/10.12677/AP.2018.811191}{Paper}]
% \end{etaremune}

\medskip

\begin{rSection}{Invited Talks}
\textbf{Managing the Shift in Phishing Attack to Telephone Based Phishing}\\
Panelist, APWG eCrime 2024, Boston, (Sept, 2024.)\\ 

\item 
\textbf{Go Viral and Go Toxic: the Use and Abuse of Social Media }\\
Workshop of 2023 EECS Rising Star, Gatech, (Nov, 2023.)\\
Security Privacy Interaction Lab, University of Michigan, (Nov, 2023.)\\
% University of Texas, San Antonio, (Jan, 2024)\\
% University of Mississippi, (Jan, 2024)\\
% University of Louisiana, (Jan, 2024)\\
% University of Wyoming, (Jan, 2024)\\
% CISPA, (Feb, 2024.)\\
% NYU Shanghai, (Feb, 2024.)\\
% NYU Tandon, (Mar, 2024.)\\
% Arizona State University, (Mar, 2024.)\\
% University of Houston, (Mar, 2024)\\
% Indiana University Bloomington, (Mar, 2024.)
\item 


\item 
\textbf{Digitally Speaking: The Perks \& Perils, Zoombombing.}\\
 The Friday Power Lunch (5-14-2021) by Network NOVA, (May, 2021.)\\
\href{https://www.youtube.com/watch?v=JB6-rnlVD6g&t=8s}{[Recording]} 
\item 
\textbf{Prejudice and Ignorance.}\\
Panelist, The Neureality, (Apr, 2021.)\\
\href{https://www.bilibili.com/video/BV1py4y1b7d8/}
{[Recording]} 
\item 
\textbf{Dissecting the Meme Magic: Understanding Indicators of Virality in Image Memes.}\\
The Hmm @ IMPAKT, (Feb, 2021.)\\
\href{https://impakt.nl/events/2021/conversation/the-hmm-impakt/}{[Recording]}
% \item 
% \textbf{[Paper Talk]}\\
% Examining the Impact of Social Distance on Reactions Towards Sulli’s
% Death on Twitter.\\
% Workshop on Cyber Social Threats (CySoc), (Jun, 2020)\\
\end{rSection}

\medskip

\begin{rSection}{Teaching}
\item \textbf{INFO-I130: Introduction to Cybersecurity, }Indiana University\hfill Fall 2024
\\Instructor, class size = 50
\item \textbf{EK 103: Computational Linear Algebra, }Boston University \hfill Fall 2021
\\Teaching Assistant, class size = 84
\item \textbf{EC 521: Cybersecurity, }Boston University \hfill Fall 2020
\\Teaching Assistant, class size = 41
\end{rSection}

\medskip


\begin{rSection}{Mentorship and Supervision}
\item \textbf{PhD Students}\\
Muwu Shan.
\hfill 2024 -\\
Weihong Qi, PhD rotation. 
\hfill 2024 -
\item \textbf{BS Students}\\
Anushka Dave.
\hfill 2024 -\\
Chuck Griffin Segal.
\hfill 2024 -\\
Dominic J Theodoropoulos.
\hfill 2024 -\\
Luis Abrego.
\hfill 2024 -\\

\end{rSection}

\medskip

\begin{rSection}{Service}
\item \textbf{PC Member} CCS \hfill 2024
\item \textbf{PC Member} Euro S\&P \hfill 2024
\item \textbf{Reviewer} Journal of Big Data \hfill 2024
\item \textbf{Reviewer} Scientific Reports \hfill 2024
\item \textbf{Reviewer} Injury Epidemiology \hfill 2024
\item \textbf{Reviewer} Knowledge and Information Systems \hfill 2024
\item \textbf{Reviewer} Social Network Analysis and Mining \hfill 2024
\item \textbf{Reviewer} IC2S2 \hfill 2024
\item \textbf{Reviewer} CHI \hfill 2024
\item \textbf{Reviewer} Telematics and Informatics Reports \hfill 2024
\item \textbf{PC Member} ICWSM \hfill 2023 -  current
\item \textbf{Reviewer} ICWSM \hfill 2022 - current
\item \textbf{Reviewer} CSCW \hfill 2021 - current
\item \textbf{PC Member} Truth \& Trust Online Conference (TTO) \hfill 2022
\item \textbf{Reviewer} Asia Pacific Journal of Education \hfill 2022
\item \textbf{Reviewer} Journal of Business Research \hfill 2021
\item \textbf{Mentor} Graduate Women in Science and Engineering (GWISE) 
\hfill 2020 - 2024
\end{rSection}

\medskip

\begin{rSection}{Translated Books}
\item Deesha Philyaw (2023), 
(\textbf{C. Ling}, Trans).\\
\textit{The Secret Lives of Church Ladies}\\
Hunan Literature and Art Publishing House. (Original work was published in 2020.)
\newline[\href{https://book.douban.com/subject/36504518/}{Book}]

\item Sakamoto, P. R. (2021), 
(\textbf{C. Ling}, Trans).\\
\textit{Midnight in Broad Daylight: a Japanese American family caught between two worlds}\\
Shanghai: Sanlian. (Original work was published in 2016.)
\newline[\href{https://book.douban.com/subject/35476851/}{Book}]

\item Gordon W. Allport (2020), (\textbf{C. Ling}, Trans). \\
\textit{The Nature of Prejudice}\\
Beijing: Hina. (Original work was published in 1954).
\newline[\href{https://book.douban.com/subject/35220441/}{Book}]

\item Jamie James (2019), (\textbf{C. Ling}, Trans).\\
\textit{Pop Art }\\
Beijing: Hina. (Original work was published in 1996).
\newline[\href{https://book.douban.com/subject/30291202/}{Book}]


% \clearpage


% \begin{rSection}{References}
% \item \textbf{Professor Gianluca Stringhini}\\
% Associate Professor, Department of Electrical and Computer Engineering, Boston University\\
% 8 St. Mary’s Street Boston, MA 02215, Room 331\\
% gian@bu.edu\\

% \item \textbf{Professor Jeremy Blackburn}\\
% Associate Professor, Department of Computer Science, Binghamton University\\
% Binghamton University, State University of New York,
% Binghamton, NY 13900, EB N10\\
% jblackbu@binghamton.edu\\

% \item \textbf{Professor Emiliano De Cristofaro}\\
% Professor, Computer Science \& Engineering Department, University of California, Riverside
% \\
% 351 Winston Chung Hall, University of California Riverside, CA 92521
% \\
% emiliano.decristofaro@ucr.edu\\
% \end{rSection}
\end{rSection}
\end{document}
